IT Spillovers in Long-Run TFP \\ A SVAR Approach

### 2018-01-30 Latex/Dissertation_Workshop_23Jan2018/dw23jan2018.tex
basu presentation and some literature note-taking

@@

Intermediate good $s$ is Cobb-Douglas with exogenous TFP $\Psi_t$:
\begin{equation}
Y_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
\end{equation}

@@

@@

 $\rightarrow$ to a Barsky \& Sims-type identification, the two shocks are observationally equivalent!

 $\Rightarrow$ econometric challenge is to disentangle the two!

@@

Intuition:
\begin{itemize}
\item News shock makes all sectors of the economy more productive $\rightarrow$ impacts the sectoral price $P^IT$ as well as P $\Rightarrow$ relative prices do not move.
\item IT productivity shock makes only the IT sector more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ \textbf{only} $\Rightarrow$ relative prices move! 
\end{itemize}

@@

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{From reduced form to structural form}
	\label{identification}

Innovation in TFP at time $t$ can be decomposed as:

\begin{equation}
\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
\end{equation}

    \begin{enumerate}
    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters (enough for prices to adjust, so 6-12);

    \item The IT productivity shock maximizes the remaining FEV of future TFP;

@@

	\item Replace IT prices with capital prices (following Comin \& Gertler)
	\end{itemize}

>>>>

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{VARs - A quick recap}
	\label{identification}

@@

Intermediate good $s$ is Cobb-Douglas with exogenous TFP $\Psi_t$:
\begin{equation}
Y^M_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
\end{equation}

@@

So in this model, the innovation to TFP at period $t$ is:
\begin{equation}
\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
\end{equation}

@@

@@

Intuition:
\begin{itemize}
\item News shock makes all sectors of the economy more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ as well as P $\Rightarrow$ relative prices do not move.
\item IT productivity shock makes only the IT sector more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ \textbf{only} $\Rightarrow$ relative prices move! 
\end{itemize}

@@

Recall that the innovation in TFP at time $t$ is:

\begin{equation*}
\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
\end{equation*}

    \begin{enumerate}
    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP, with a zero impact effect, subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters;

    \item The IT productivity shock maximizes the remaining FEV of future TFP, with a zero impact effect;

@@

@@

	\item Replace IT prices with capital prices (following Comin \& Gertler)

	\item Replace CPI inflation with PCE inflation
	\end{itemize}
